---
title: "Using SDMWorkflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using SDMWorkflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of SDMWorkflows is to make a workflow for Species distribution models for Sustainscapes

## Installation

You can install the development version of SDMWorkflows like so:

``` r
remotes::install_github("derek-corcoran-barrios/SDMWorkflows")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SDMWorkflows)
## basic example code
```

We will start by generating a list of species to be checked

```{r SppeciesCheck}
Spp <- c("Abies concolor", "Abies lowiana", "Canis lupus", "Cannis lupus")
```

In this case we have four taxa to check, however we know that *Abies concolor* and *Abies lowiana* are synonyms for the accepted name of *Abies concolor* and that the second version of *Canis lupus* is badly written, it would be expected that the `Clean_Taxa()` function will recognize that there are only 2 species here and return a data frame with these together with their taxonomy resolution,

```{r}
Final_List <- Clean_Taxa(Spp)
```

Which yields the following table, the resolved species is the Species Column

```{r, echo = F}
knitr::kable(Final_List)
```

